Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-06 manuscripts/manuscript.Rmd
revise sensitivity latin hypercube

```{r sensitivity-calc}
source("components/sensitivity.R")
sensitivity_dat <- dat
```

```{r figure_S9, fig.height=6, fig.width=6, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histogram shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=simulation)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/sensitivity_dat.csv")

>>>>

```{r sensitivity-calc}
source("components/sensitivity.R")

models <- c("Myers","Allen")

parameters <- list(
  Myers = list(
    c(r=1.5 + rnorm(1, 0, 1), theta=2.5 + rnorm(1, 0, 1), K=10 + rnorm(1, 0, 1)),
    c(r=1.5 + rnorm(1, 0, 1), theta=2.5 + rnorm(1, 0, 1), K=10 + rnorm(1, 0, 1))),
  Allen = list(
    c(r=2 + rnorm(1, 0, 1), K=10 + rnorm(1, 0, 1), C=4 + rnorm(1, 0, 1)),
    c(r=2 + rnorm(1, 0, 1), K=10 + rnorm(1, 0, 1), C=4 + rnorm(1, 0, 1)))
)
nuisance_pars <- c("sigma_g")
nuisance_values <- list(sigma_g = c(0.01, 0.05))

model <- "Allen"
allen1.01 <- sensitivity(model, 
                   parameters = parameters[[model]][[1]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[1]), 
                   seed=c(1111, 2222, 3333))
allen2.01 <- sensitivity(model, 
                   parameters = parameters[[model]][[2]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[1]), 
                   seed=c(1111, 2222, 3333))
allen1.05 <- sensitivity(model, 
                   parameters = parameters[[model]][[1]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[2]), 
                   seed=c(1111, 2222, 3333))
allen2.05 <- sensitivity(model, 
                   parameters = parameters[[model]][[2]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[2]), 
                   seed=c(1111, 2222, 3333))

model <- "Myers"
Myers1.01 <- sensitivity(model, 
                   parameters = parameters[[model]][[1]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[1]), 
                   seed=c(1111, 2222, 3333))
Myers2.01 <- sensitivity(model, 
                   parameters = parameters[[model]][[2]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[1]), 
                   seed=c(1111, 2222, 3333))
Myers1.05 <- sensitivity(model, 
                   parameters = parameters[[model]][[1]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[2]), 
                   seed=c(1111, 2222, 3333))
Myers2.05 <- sensitivity(model, 
                   parameters = parameters[[model]][[2]], 
                   nuisance = c(sigma_g = nuisance_values$sigma_g[2]), 
                   seed=c(1111, 2222, 3333))

## Assemble into data.frame
allen_dat <- rbind(allen1.01, allen1.05, allen2.01, allen2.05) 
m <- rbind(Myers1.01, Myers1.05, Myers2.01, Myers2.05)
myers_dat <- m[c(1:2,4,3,5:8)]
names(myers_dat) <- names(allen_dat)
model_dat <- rbind(allen_dat, myers_dat)
dat <- model_dat
dat$pars.r <- factor(dat$pars.r, labels=c("A", "B", "C", "D"))
dat <- dat[c(1:2,5:6, 8, 7)]
dat$noise <- factor(dat$noise)
names(dat) <- c("model", "parameters", "replicate", "simulation", "noise", "value")

## Extract acutal parameter values corresponding to each parameter set
p1 = levels(factor(model_dat$pars.r))
p2 = levels(factor(model_dat$pars.K))
p3 = levels(factor(model_dat$pars.C))

setA = as.numeric(c(r = p1[1], K = p2[1], theta = p3[1]))
setB = as.numeric(c(r = p1[2], K = p2[2], theta = p3[2])
setC = as.numeric(c(r = p1[3], K = p2[3], C = p3[3]))
setD = as.numeric(c(r = p1[4], K = p2[4], C = p3[4]))
AllenParameterSets <- rbind(setA, setB)
MyersParameterSets <- rbind(setC,setD)

sensitivity_dat <- dat
```

```{r figure_S9, fig.height=6, fig.width=10, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histograms shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values of 1 indicate optimal performance. Columns indicate different models, rows different noise levels, and colors indicate the parameter set used. Grouped over stochastic replicates applying the contol policy and stochastic replicates of training data generated from the model indicated, see raw data for details. Randomly chosen parameter values for the models shown in tables below."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=parameters)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/sensitivity_dat.csv") 
```

```{r}
pandoc.table(AllenParameterSets, caption="Randomly chosen parameter sets for the Allen models in Figure S9." )
```
```{r}
pandoc.table(AllenParameterSets, caption="Randomly chosen parameter sets for the Myers models in Figure S9." )
```
